Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-10-25 jssst/paper.tex
add software journal
Add related work (ChaiScript)

% Sample file for the use of compsoft style file.
%
\documentclass[S,R,E]{article/compsoft}

% Preamble
%
% 「コンピュータソフトウェア」誌に掲載される論文の場合，次で
% 巻数，号数，開始ページ，終了ページを指定する．
\volNoPp{29}{1}{78}{84}

@@

% 論文のタイトル
\title{Lightweight Ruby Framework\\ for Improving Embedded Software Efficiency}

% 著者
% 和文論文の場合，姓と名の間には半角スペースを入れ，
% 複数の著者の間は全角スペースで区切る
%
\author{Takuro Yamamoto　Hiroshi Oyama　Takuya Azumi}
%
% ここにタイトル英訳 (英文の場合は和訳) を書く．
%
\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発フレームワーク}
%
% ここに著者英文表記 (英文の場合は和文表記) および
% 所属 (和文および英文) を書く．
% 複数著者の所属はまとめてよい．
%
\shozoku{山本　拓朗, 安積　卓也}{大阪大学大学院基礎工学研究科}%
{Graduate School of Engineering Science, Osaka University}
\shozoku{大山　博司}{オークマ株式会社}%
{OKUMA Corporation}

%
% 出典情報は \shutten とすれば出力される．
\shutten
%
% 受付年月日，記事カテゴリなどは自動的に生成される．
\uketsuke{2011}{12}{15}
%
% その他，脚注に入れるものがあれば，¥note に記述する．
%\note{脚注に入れる内容}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=14cm,clip]{figure/proposed.eps}
    \caption{System model of the proposed framework}
    \label{fig:proposed}
\end{figure*}

@@

\begin{table}[t]
    \centering
\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
    %\scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
          Compile Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{C and CDL file code for the number of RiteVMs}
    %\scriptsize
    {\tabcolsep=0.2cm
    \begin{tabular}{c||c|c|c}
                & (A)       & (B)     & Diff  \\ \hline
        C (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    }
    \label{tab:codesize}
\end{table}

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

@@

\section{Results of Research}
\label{sec:}
The mruby on TECS framework has been certified for the official platform of ET Robocon 2016.
In addition, the proposed framework on LEGO MINDSTORMS EV3 has been commercialized by Afrel Co., Ltd.

>>>>

% Sample file for the use of compsoft style file.
%
\documentclass[S,R,E]{article/compsoft}
% Preamble
%
% 「コンピュータソフトウェア」誌に掲載される論文の場合，次で
% 巻数，号数，開始ページ，終了ページを指定する．
\volNoPp{0}{0}{0}{0}

@@

% 論文のタイトル
\title{Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development}

% 著者
% 和文論文の場合，姓と名の間には半角スペースを入れ，
% 複数の著者の間は全角スペースで区切る
%
\author{Takuro Yamamoto　Hiroshi Oyama　Takuya Azumi}
%
% ここにタイトル英訳 (英文の場合は和訳) を書く．
%
\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発コンポーネントベースフレームワーク}
%
% ここに著者英文表記 (英文の場合は和文表記) および
% 所属 (和文および英文) を書く．
% 複数著者の所属はまとめてよい．
%
\shozoku{山本　拓朗, 安積　卓也}{大阪大学大学院基礎工学研究科}%
{Graduate School of Engineering Science, Osaka University}
\shozoku{大山　博司}{オークマ株式会社}%
{OKUMA Corporation}

%
% 出典情報は \shutten とすれば出力される．
\shutten
%
% 受付年月日，記事カテゴリなどは自動的に生成される．
\uketsuke{0000}{00}{00}
%
% その他，脚注に入れるものがあれば，¥note に記述する．
%\note{脚注に入れる内容}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/proposed.eps}
    \caption{System model of the proposed framework}
    \label{fig:proposed}
\end{figure}

@@

\begin{table}[t]
    \centering
\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                        & App\&Lib     & App        &   App\&Lib/App  \\ \hline
        Bytecode Size   & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
        Loading Time    & 305.081 msec & 7.774 msec &   $\times$39.2          \\
        Compile Time    & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{C and CDL file code for the number of RiteVMs}
    \footnotesize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                       & (A)       & (B)     & Diff  \\ \hline
        C (Total)          & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{ $\alpha$ : the number of RiteVMs}
    \end{tabular}
    }
    \label{tab:codesize}
\end{table}

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, ChaiScript\cite{url:ChaiScript}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
It is a dialect of ECMAScript (a.k.a. JavaScript).
ChaiScript is header only, that is, it only needs to include the header files in order to use it in an application.
ChaiScript will support co-routines, but not now.

@@

\section{Results of Research}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/}.

In addition, the proposed framework on LEGO MINDSTORMS EV3 has been commercialized for education by Afrel Co., Ltd\footnote{http://www.afrel.co.jp/lineup/textset (in Japanese)}, which is an official partner of LEGO Education.
